quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-14 paper-quollr.Rmd
Added setence with linked plots
slight addition to application sentence

@@

2. Because $6$ clusters are hard to examine together, use the menu to select just one cluster to view at at time. Selecting just cluster $1$ might help you see the explanation above, that a small group is quite separate from the main group. This suggests both the layouts and the clustering that groups these together might be wrong. Now change to focus on cluster $5$ (yellow). This group is a fairly large sparse cluster but it is separated from the other points. Both layouts are right in separating these points from the others.

>>>>

In addition to `langevitour`, linked plots can also be constructed using tour views generated with the `detourr` package. (see [vignette: 8. Linked plots with `detourr`](https://jayanilakshika.github.io/quollr/articles/quollr8linkeddetourr.html) for details.)

@@

2. Because $6$ clusters are hard to examine together, use the menu to select just one cluster to view at at time. Selecting just cluster $1$ might help you see the explanation above, that a small group is quite separate from the main group. This suggests both the layouts and the clustering that groups these together might be wrong. Now change to focus on cluster $5$ (yellow). This group is a fairly large sparse cluster but it is separated from the other points. Both layouts are right in separating these points from the others but the fit for layout f is slightly better.

### 2025-12-14 paper-quollr.tex
Added setence with linked plots
slight addition to application sentence

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Examine the model in the data space for each, by looking at the tour views. In each case, the clustering doesn't quite match the separations in the data, and both models help see this. For example, the orange cluster (\(1\)) should probably be split into more than one cluster because both models show large stretched lines connecting a small group far from the remaining orange points.
\item
  Because \(6\) clusters are hard to examine together, use the menu to select just one cluster to view at at time. Selecting just cluster \(1\) might help you see the explanation above, that a small group is quite separate from the main group. This suggests both the layouts and the clustering that groups these together might be wrong. Now change to focus on cluster \(5\) (yellow). This group is a fairly large sparse cluster but it is separated from the other points. Both layouts are right in separating these points from the others.
\item
  To examine where the layouts differ, examine clusters \(4\) (green) and \(6\) (cream), by selecting just these two. Layout a has them close, but layout f has them far apart. (It might also help to include cluster \(5\) here because layout a has this group close to the cluster \(4\) also). In the tour view, we can see that they three clusters are separated clusters in different directions away from the most of the other points. They are both correct in this. It may have been better to place them all in different corners of the layout, but they have preserved the most important aspect that they are separated clusters. That they are all close together in layout a could be incorrectly interpreted as close in high-dimensions though.
\end{enumerate}

>>>>

In addition to \texttt{langevitour}, linked plots can also be constructed using tour views generated with the \texttt{detourr} package. (see \href{https://jayanilakshika.github.io/quollr/articles/quollr8linkeddetourr.html}{vignette: 8. Linked plots with \texttt{detourr}} for details.)

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Examine the model in the data space for each, by looking at the tour views. In each case, the clustering doesn't quite match the separations in the data, and both models help see this. For example, the orange cluster (\(1\)) should probably be split into more than one cluster because both models show large stretched lines connecting a small group far from the remaining orange points.
\item
  Because \(6\) clusters are hard to examine together, use the menu to select just one cluster to view at at time. Selecting just cluster \(1\) might help you see the explanation above, that a small group is quite separate from the main group. This suggests both the layouts and the clustering that groups these together might be wrong. Now change to focus on cluster \(5\) (yellow). This group is a fairly large sparse cluster but it is separated from the other points. Both layouts are right in separating these points from the others but the fit for layout f is slightly better.
\item
  To examine where the layouts differ, examine clusters \(4\) (green) and \(6\) (cream), by selecting just these two. Layout a has them close, but layout f has them far apart. (It might also help to include cluster \(5\) here because layout a has this group close to the cluster \(4\) also). In the tour view, we can see that they three clusters are separated clusters in different directions away from the most of the other points. They are both correct in this. It may have been better to place them all in different corners of the layout, but they have preserved the most important aspect that they are separated clusters. That they are all close together in layout a could be incorrectly interpreted as close in high-dimensions though.
\end{enumerate}
